---
title: "Questionnaire exploration"
description: |
  A new article created using the Distill format.
author:
  - name: Carlos Cámara-Menoyo
    url: https://carloscamara.es/
    affiliation: University of Warwick
    affiliation_url: https://warwick.ac.uk
    orcid_id: 0000-0002-9378-0549
  - name: Tessio Novack
    affiliation: University of Warwick
    affiliation_url: https://warwick.ac.uk 
    orcid_id: 0000-0003-2817-5972
  - name: James Tripp
    affiliation: University of Warwick
    affiliation_url: https://warwick.ac.uk 
    orcid_id: 0000-0003-2471-3411 
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 2
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(flexdashboard)
library(dplyr)
library(forcats)
library(ggplot2)
library(readr)
library(reactable)
library(stringr)
library(tidyr)

# Loads all the files where functions are defined
files <- list.files(path = here::here("R"), pattern = "*.R", full.names = TRUE,
                    recursive = FALSE)
for (i in files) {
  source(i)
}


#  Data processing ---------------------------------------------------

df <- read_csv(here::here("data/output/survey_clean.csv")) %>% 
  filter(group != "Public") 

ratings_df <- get_image_ratings(df)
                                
# Get rid of neutral ratings, to force meaningful results.            
# ratings_df <- get_image_ratings(df) %>%
#   filter(rating != "Neutral") %>%
#   mutate(rating = fct_drop(rating)) %>%
#   mutate(rating_n = as.numeric(rating))

ratings_total <- ratings_df %>% 
  count(image_num)

n_rated_max <- max(ratings_total$n)
n_rated_min <- min(ratings_total$n)
n_rated_mean <- round(mean(ratings_total$n),2)

# Color definitions ------------------------------------------

warwick_color <- "#5B3069"
warwick_color_disabled <- "#E7E6F7"

# Check this palette: https://bootswatch.com/pulse/

primary_disabled <- "#9278BA"
secondary_disabled <- "#DFDFDF"


# thematic::thematic_rmd()

```

```{r ggplot_defaults}

# Custom ggplot theme.
mytheme_minimal <- theme_minimal(base_size = 12) +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        plot.caption = element_text(size = 8, face = "italic", 
                                    colour = "grey60"),
        plot.subtitle = element_text(size = 9, face = "plain", 
                                     colour = "grey50"),
        axis.ticks = element_line(colour = "grey80"),
        axis.ticks.length = unit(2, "pt"),
        strip.text = element_text(size = 12))
mytheme <- theme_minimal(base_size = 12) +
  theme(plot.caption = element_text(size = 8, face = "italic", 
                                    colour = "grey60"),
        plot.subtitle = element_text(size = 9, face = "plain", 
                                     colour = "grey50"),
        axis.ticks = element_line(colour = "grey80"),
        axis.ticks.length = unit(2, "pt"),
        strip.text = element_text(size = 12))
theme_set(mytheme_minimal)
```

# Introduction

Explain the questionnaire, type of questions, data collection.

We are analysing **`r nrow(df)` responses** from a questionnaire published between `r min(df$start_date)` and `r max(df$start_date)`.

Respondents were selected following these groups: `r levels(as.factor(df$group))`

# Research questions

-   Does demographics influence in the perceived walkability?

    -   Are some demographics more decisive than others?

-   Does location influence the ratings?

-   Does our clusters' classification influence perceived walkability?

    -   Do they work?

# Results

## Overall

In this section we are showing results without aggregation.

```{r histogram-overall, fig.cap="Histogram of ratings (no aggregation)"}
ggplot(ratings_df, aes(rating_n)) +
  geom_histogram(binwidth = 1) +
  facet_wrap(~item, ncol = 4) +
  labs(title = "Perceived walkability by item (overall)",
       subtitle = "Ratings range from Strongly Disagree (1) to Strongly Agree (5)",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "",
       y = NULL) 


```

```{r ratings-overall, fig.cap="Overall distribution of ratings by walkability item"}
ggplot(ratings_df, aes(x = rating_n, y = item)) +
  geom_boxplot() +
  labs(title = "Perceived walkability by item (overall)",
       subtitle = "Ratings range from Strongly Disagree (1) to Strongly Agree (5)",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = NULL,
       y = NULL) 
```

Figure \@ref(fig:histogram-overall) shows that ...

Figure \@ref(fig:ratings-overall) shows that vibrancy, safety and enjoyment have the same mean (Neutral), whereas aesthetics' mean is lower (Disagree).
Furthermore, vibrancy and enjoyment seem to have a similar distribution in ratings, suggesting that, either people do no differentiate between these two concepts or they were ill-defined.

## Perceptions by demographics

In this section we will be aggregating ratings by gender, age, ethnicity, sexual orientation, immigration background, disabilities affecting mobility, and local knowledge.
By doing so, we expect to identify some demographics that are more relevant than others

TODO: combine more than one demographic?

### By Gender

The table below shows age distribution

```{r, fig.cap="Number of respondents per genre"}
counts_df <- df %>% 
  count(gender) %>% 
  mutate(gender = as.factor(gender))

knitr::kable(counts_df,
             caption = "Number of respondents per genre")
```

```{r histogram-gender, fig.cap="Ratings by genre (histogram)", fig.height=7}
ggplot(ratings_df, aes(rating_n, fill = gender)) +
  geom_histogram(binwidth = 1) +
  facet_grid(gender ~ item) +
  labs(title = "Perceived walkability by gender",
       subtitle = "Ratings range from Strongly Disagree (1) to Strongly Agree (5)",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "",
       y = NULL) +
  scale_fill_brewer(palette="Set1") +
  theme(legend.position="top") 


```

```{r ratings-gender, fig.cap="Ratings by genre (boxplot)"}

ggplot(ratings_df, aes(x = rating_n, y = gender, fill = gender)) +
  geom_boxplot() +
  facet_wrap(~item) + 
  # theme_minimal() + 
  scale_fill_brewer(palette="Set1") +
  theme(legend.position="none") + 
  labs(title = "Perceived walkability by gender",
       subtitle = "Ratings: Strongly Disagree (1) - Strongly Agree (5)",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "",
       y = NULL) +
  geom_text(data = counts_df, aes(x = 3, label = paste0("N: ", n)),
            size = 3)
  
```

Figure \@ref(fig:ratings-gender) suggests that there are no big differences between male and female, as both groups follow a similar distribution.
However, when comparing it to Figure \@ref(fig:ratings-gender), we can see that female's ratings towards safety are notably lower than any other gender.

To a lesser extent, there are some differences in how aesthetics are perceived for non-binary and those who do not fit in the previous categories), who seem to...

### By Age

The table below shows age distribution

```{r, fig.cap="Number of respondents per age"}
counts_df <- df %>% 
  count(age) %>% 
  mutate(age = as.factor(age))

knitr::kable(counts_df,
             caption = "Number of respondents per age")
```

```{r histogram-age, fig.cap="Ratings by age (histogram)", fig.height=7}
ggplot(ratings_df, aes(rating_n, fill = age)) +
  geom_histogram(binwidth = 1) +
  facet_grid(age ~ item) +
  labs(title = "Perceived walkability by gender",
       subtitle = "Ratings range from Strongly Disagree (1) to Strongly Agree (5)",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "",
       y = NULL) +
  scale_fill_brewer(palette="Blues") +
  theme(legend.position="top") 


```

```{r ratings-age, fig.cap="Ratings by age"}

ggplot(ratings_df, aes(x = rating_n, y = age, fill = age)) +
  geom_boxplot() +
  facet_wrap(~item) + 
  # theme_minimal() + 
  scale_fill_brewer(palette="Blues") +
  theme(legend.position="none") + 
  labs(title = "Perceived walkability by age",
       subtitle = "Ratings: Strongly Disagree (1) - Strongly Agree (5)",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = NULL,
       y = NULL)
```

The older we get, the less aesthetically appealing we find streets.
No significant differences in enjoyment.
Safety: only young adults seem to feel safer (probably they feel safer and more confindent in every aspect of their lifes?), then those between 35-44.
At 65, ratings are more skewed towards lower values.

### By ethnicity

The table below shows ethnicity distribution


```{r, fig.cap="Number of respondents per ethnicity"}
counts_df <- df %>% 
  count(ethnicity) 

knitr::kable(counts_df,
             caption = "Number of respondents per ethnicity")
```

```{r histogram-ethnicity, fig.cap="Ratings by ethnicity (histogram)", fig.height=7}
ggplot(ratings_df, aes(rating_n, fill = ethnicity)) +
  geom_histogram(binwidth = 1) +
  facet_grid(ethnicity ~ item) +
  labs(title = "Perceived walkability by ethnicity",
       subtitle = "Ratings range from Strongly Disagree (1) to Strongly Agree (5)",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "",
       y = NULL) +
  scale_fill_brewer(palette="Set1") +
  theme(legend.position="top") 


```


```{r ratings-ethnicity, fig.cap="Ratings by ethnicity"}

ggplot(ratings_df, aes(x = rating_n, y = ethnicity, fill = ethnicity)) +
  geom_boxplot() +
  facet_wrap(~item) + 
  # theme_minimal() + 
  scale_fill_brewer(palette="Set1") +
  theme(legend.position="none") + 
  labs(title = "Perceived walkability by ethnicity",
       subtitle = "",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "Ratings: Strongly Disagree (1) - Strongly Agree (5)",
       y = NULL)
```

I wouldn't have imagined that black people would be those who perceived streets safer!

### By sexual orientation

```{r, fig.cap="Number of respondents per sexual orientation"}
counts_df <- df %>% 
  count(sexual_orientation_selected_choice) 

knitr::kable(counts_df,
             caption = "Number of respondents per sexual orientation")
```

```{r histogram-sexual-orientation, fig.cap="Ratings by sexual orientation (histogram)", fig.height=7}
ggplot(ratings_df, aes(rating_n, fill = sexual_orientation_selected_choice)) +
  geom_histogram(binwidth = 1) +
  facet_grid(sexual_orientation_selected_choice ~ item) +
  labs(title = "Perceived walkability by sexual orientation",
       subtitle = "Ratings range from Strongly Disagree (1) to Strongly Agree (5)",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "",
       y = NULL) +
  scale_fill_brewer(palette="Set1") +
  theme(legend.position="top") 


```



```{r ratings-sexual-orientation, fig.cap="Ratings by Sexual orientation"}

ggplot(ratings_df, aes(x = rating_n, y = sexual_orientation_selected_choice, 
                       fill = sexual_orientation_selected_choice)) +
  geom_boxplot() +
  facet_wrap(~item) + 
  # theme_minimal() + 
  scale_fill_brewer(palette="Set1") +
  theme(legend.position="none") + 
  labs(title = "Perceived walkability by sexual orientation",
       subtitle = "",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "Ratings: Strongly Disagree (1) - Strongly Agree (5)",
       y = NULL)
```

I believe we should combine some categories: gay + queer for sure, and probably gay + queer + lesbian into homosexual?

### By immigration status

```{r, fig.cap="Number of respondents per immigration background"}
counts_df <- df %>% 
  count(immigration_background) 

knitr::kable(counts_df,
             caption = "Number of respondents per immigration background")
```

```{r histogram-immigration-background, fig.cap="Ratings by immigration background (histogram)", fig.height=7}
ggplot(ratings_df, aes(rating_n, fill = immigration_background)) +
  geom_histogram(binwidth = 1) +
  facet_grid(immigration_background ~ item) +
  labs(title = "Perceived walkability by immigration background",
       subtitle = "Ratings range from Strongly Disagree (1) to Strongly Agree (5)",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "",
       y = NULL) +
  scale_fill_brewer(palette="Set1") +
  theme(legend.position="top") 


```


```{r immigrants, fig.cap="Ratings by immigration background"}

ggplot(ratings_df, aes(x = rating_n, y = immigration_background, 
                       fill = immigration_background)) +
  geom_boxplot() +
  facet_wrap(~item) + 
  # theme_minimal() + 
  scale_fill_brewer(palette="Set1") +
  theme(legend.position="none") + 
  labs(title = "Perceived walkability by immigration background",
       subtitle = "",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "Ratings: Strongly Disagree (1) - Strongly Agree (5)",
       y = NULL)
```

TODO: rename "yes" -> Immigration background, no -> "?"

I didn't expected to see that people with immigration backgrounds perceive streets to be safer.

### By disabilities


```{r, fig.cap="Number of respondents per immigration background"}
counts_df <- df %>% 
  count(mobility_disabilities) 

knitr::kable(counts_df,
             caption = "Number of respondents per immigration background")
```

```{r histogram-disabilities, fig.cap="Ratings by immigration background (histogram)", fig.height=7}
ggplot(ratings_df, aes(rating_n, fill = mobility_disabilities)) +
  geom_histogram(binwidth = 1) +
  facet_grid(mobility_disabilities ~ item) +
  labs(title = "Perceived walkability by immigration background",
       subtitle = "Ratings range from Strongly Disagree (1) to Strongly Agree (5)",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "",
       y = NULL) +
  scale_fill_brewer(palette="Set1") +
  theme(legend.position="top") 


```


```{r disabilities, fig.cap="Ratings by disabilities affecting mobility"}

ggplot(ratings_df, aes(x = rating_n, y = mobility_disabilities, 
                       fill = mobility_disabilities)) +
  geom_boxplot() +
  facet_wrap(~item) + 
  # theme_minimal() + 
  scale_fill_brewer(palette="Set1") +
  theme(legend.position="none") + 
  labs(title = "Perceived walkability by disabilities affecting mobility",
       subtitle = "Yes = Have a disability affecting their mobility",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "Ratings: Strongly Disagree (1) - Strongly Agree (5)",
       y = NULL)
```

### By local knowledge

TODO: sort answers by correct order (0-4) in the data preparations' file.

```{r, fig.cap="Number of respondents per local knowledge"}
counts_df <- df %>% 
  count(local_knowledge_london) 

knitr::kable(counts_df,
             caption = "Number of respondents per immigration background")
```

```{r histogram-local-knowledge, fig.cap="Ratings by local knowledge (histogram)", fig.height=7}
ggplot(ratings_df, aes(rating_n, fill = local_knowledge_london)) +
  geom_histogram(binwidth = 1) +
  facet_grid(local_knowledge_london ~ item) +
  labs(title = "Perceived walkability by immigration background",
       subtitle = "Ratings range from Strongly Disagree (1) to Strongly Agree (5)",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "",
       y = NULL) +
  scale_fill_brewer(palette="Set1") +
  theme(legend.position="top") 


```


```{r local-knowledge, fig.cap="Ratings by London's local knowledge"}

ggplot(ratings_df, aes(x = rating_n, y = local_knowledge_london, 
                       fill = local_knowledge_london)) +
  geom_boxplot() +
  facet_wrap(~item) + 
  # theme_minimal() + 
  scale_fill_brewer(palette="Set1") +
  theme(legend.position="none") + 
  labs(title = "Perceived walkability by local knowledge",
       subtitle = "All images were from London locations",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "Ratings: Strongly Disagree (1) - Strongly Agree (5)",
       y = NULL)
```

## Perceptions by cluster

Locations were grouped in five clusters, based exclusively in the features present in the four images of the same location, using a ML algorithm (see [repo here](https://github.com/WarwickCIM/walkability_ml)).
Location was not considered.

In this case N is the number of ratings received, and all of them received the same ratings, by design.r

```{r, fig.cap="Number of respondents per cluster"}
counts_df <- ratings_df %>% 
  count(cluster) 

knitr::kable(counts_df,
             caption = "Number of respondents per cluster")
```

```{r histogram-ckuster, fig.cap="Ratings by cluster (histogram)", fig.height=7}
ggplot(ratings_df, aes(rating_n, fill = cluster)) +
  geom_histogram(binwidth = 1) +
  facet_grid(cluster ~ item) +
  labs(title = "Perceived walkability by cluster",
       subtitle = "Ratings range from Strongly Disagree (1) to Strongly Agree (5)",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "",
       y = NULL) +
  scale_fill_brewer(palette="Set1") +
  theme(legend.position="top") 


```

```{r img-cluster, fig.cap="Ratings by Image cluster"}

ggplot(ratings_df, aes(x = rating_n, y = cluster, 
                       fill = cluster)) +
  geom_boxplot() +
  facet_wrap(~item) + 
  # theme_minimal() + 
  scale_fill_brewer(palette="Set1") +
  theme(legend.position="none") + 
  labs(title = "Perceived walkability by cluster",
       subtitle = "All images were from London locations",
       caption = "Source: Survey (Novack, Tripp, Cámara-Menoyo 2022)",
       x = "Ratings: Strongly Disagree (1) - Strongly Agree (5)",
       y = NULL)
```

## Perceptions by geographic area

```{r layout="l-screen-inset"}
library(leaflet)
leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lat=51.5076, lng=-0.1281, popup="Dummy marker")
```

(Reference <https://cengel.github.io/R-data-viz/domains.html#maps-e.g.-tmap>)

Tessio, since you have the location of every location, we could create a map and see:

-   if ratings respond to geographic locations (are there some areas which are less walkable than others?)

-   if there's correlation between ratings and osm tagging (i.e. `highway = primary` is always more walkable than `highway = alley` obviously, this is a stupid example, but we could use highway=\*, smoothness=\*, width=\* , or even do some spatial calculations such as distance to certain amenities, trees, parks...)

# Conclusions

I'm afraid we have bad news:

-   Usually, there are no differences between groups

-   Usually, the mean for every item is 3 (neutral) -> not very useful -> we might have used numeric values?

    -   We might want to re-scale the answers to a scale from 1-4?

-   This is true in general for every item and every social group, with few exceptions:

    -   Safety

    -   aesthetics (to a much lesser extent) -> to be explored if it differs from people within the UK and outside

-   Differences are usually spotted into groups with less participants.

-   But, what is more to me: the results seem to be random: if we generated a random set of answers we might get a similar result.
    I'm starting to question if people (especially fast responders from prolific) have answered randomly to get paid -> repeat results and filter those which have taken less than 10 minutes?

    -   Introduce some validation in qualtrics? -> i.e. timing or if answers are too similar to the random ones.

-   This might be a problem of visualisation used or the fact that the number of people -> could you think of better ones?

Plot average rating per image over time -> detect possible
